---
title: "Near-term forecasts of NEON lakes reveal gradients of environmental predictability across the U.S."
output: html_notebook
---

# Set up analysis

The analysis needs the following libraries, environment variables, and sourced R functions.

```{r}
library(tidyverse)
library(lubridate)
library(patchwork)
library(egg)
library(broom)
library(arrow)
library(dplyr)
#Sys.setenv("AWS_EC2_METADATA_DISABLED"="TRUE")
#Sys.unsetenv("AWS_ACCESS_KEY_ID")
#Sys.unsetenv("AWS_SECRET_ACCESS_KEY")
#Sys.unsetenv("AWS_DEFAULT_REGION")
#Sys.unsetenv("AWS_S3_ENDPOINT")
lake_directory <- here::here()
source(file.path(lake_directory,"workflows","neon_lakes_ms","scoring.R"))

```

# Reading in scores

The scores (i.e., metrics of how well a forecast predicts an observation) are already calculated from the forecasts using the the `workflows/neon_lakes_ms/02_score_forecasts.R` script. The following code reads the individual forecast files into memory and stacks the the scored forecasts together. The scores are located in a remote s3 bucket and are read into local memory without needing to download the files. The filtering to select only the "teams" of interest (i.e., models run) occurs remotely, thus reducing the size of the data that are transferred.

```{r}
s <- score_schema()
s3 <- s3_bucket(bucket = "scores",
                endpoint_override = "s3.flare-forecast.org",
                anonymous=TRUE)
ds <- open_dataset(s3, schema=s, format = "csv", skip_rows = 1)
combined <- ds %>% filter((team == "ms1_glm_flare" | team == "ms1_doymean") & 
                          time < as_date("2021-10-24")) %>% collect()
```

# Clean-up up table of scores

The combined table is cleaned up by renaming of the columns, defining the NEON ecoclimatic domains, expanding the model names, and defining the start of "fall" that is used in later analyses. The squared error is calculated for each forecast-observation pair.

```{r}
combined1 <- combined %>%
  rename("siteID" = theme) %>%
  mutate(resid = observed - mean,
         sq_error = (resid)^2) %>%
  select(siteID, team, time, forecast_start_time, issue_date, horizon, depth, mean, observed,sq_error, crps) %>%
  rename(Model = team) %>%
  mutate(Model = ifelse(Model == "ms1_doymean", "Day-of-year mean", Model),
         Model = ifelse(Model == "ms1_glm_flare","FLARE-GLM", Model)) %>%
  mutate(Model = factor(Model, levels = c("FLARE-GLM","Day-of-year mean")))
```

```{r}
focal_depth_top <- 0.0
focal_depth_bottom <- 1.0
focal_horizon <- 10
```

```{r}
combined2 <- combined1 %>% 
  select(siteID, Model, time, forecast_start_time, issue_date, horizon, depth, sq_error) %>%
  pivot_wider(names_from = Model, values_from = sq_error) %>%
  na.omit() %>%
  select(siteID, time, horizon, depth, `Day-of-year mean`, `FLARE-GLM`) %>% 
  pivot_longer(cols = -c("siteID","time", "horizon", "depth"), names_to = "Model",values_to = "sq_error") %>%
  pivot_wider(names_from = horizon, values_from = sq_error) %>% 
  na.omit() %>% 
  pivot_longer(cols = -c("siteID","time", "Model", "depth"), names_to = "horizon", values_to = "sq_error")

combined_top <- combined2 %>% 
  filter(depth == 0.0) %>% 
  group_by(Model, siteID, horizon) %>%  # average over siteID
  summarise(rmse = mean(sq_error, na.rm =TRUE),
            .groups = "drop") %>%
  mutate(rmse = sqrt(rmse)) %>% 
  mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG")))

combined_1m <- combined2 %>% 
  filter(depth >= focal_depth_top,
         depth <= focal_depth_bottom) %>% 
  group_by(Model, siteID, horizon) %>%  # average over siteID
  summarise(rmse = mean(sq_error, na.rm =TRUE),
            .groups = "drop") %>%
  mutate(rmse = sqrt(rmse)) %>% 
  mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG")))

combined_1m_all_sites <- combined2 %>% 
  filter(depth >= focal_depth_top,
         depth <= focal_depth_bottom) %>% 
  group_by(Model, horizon) %>%  # average over siteID
  summarise(rmse = mean(sq_error, na.rm =TRUE),
            .groups = "drop") %>%
  mutate(rmse = sqrt(rmse))

combined_all_depths <- combined2 %>% 
  group_by(Model, siteID, horizon) %>%  # average over siteID
  summarise(rmse = mean(sq_error, na.rm =TRUE),
            .groups = "drop") %>%
  mutate(rmse = sqrt(rmse)) %>% 
  mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG")))

combined_1m_crps <- combined1 %>% 
  select(siteID, Model, time, forecast_start_time, issue_date, horizon, depth, crps) %>%
  pivot_wider(names_from = Model, values_from = crps) %>%
  na.omit() %>%
  select(siteID, time, horizon, depth, `Day-of-year mean`, `FLARE-GLM`) %>% 
  pivot_longer(cols = -c("siteID","time", "horizon", "depth"), names_to = "Model",values_to = "crps") %>%
  pivot_wider(names_from = horizon, values_from = crps) %>% 
  na.omit() %>% 
  pivot_longer(cols = -c("siteID","time", "Model", "depth"), names_to = "horizon", values_to = "crps") %>% 
  filter(depth >= focal_depth_top,
         depth <= focal_depth_bottom) %>% 
  group_by(Model, siteID, horizon) %>%  # average over siteID
  summarise(crps = mean(crps, na.rm =TRUE),
            .groups = "drop") %>%
  mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG")))

```


# Building derived tables

The analysis uses a set of metric that summarize each 35-day forecast at a specific depths (the surface, 0.05m). The first is the RMSE at day 10. We choice the 10-day horizon because it XXXX. The second is the rate of change in RMSE over the first 10-days. This represents the rate that the quality of forecast degrades.

Read in lake characteristic data

```{r}
lake_info <- read_csv(file.path(lake_directory,"workflows","neon_lakes_ms", "LakeTable_15Nov2021.csv"))

variables <- tibble(variable = c("max_depth_m", "fetch_m", "volume_m3", "surface_area_km2", "mean_secchi_depth_m",
         "mean_annual_temperature_degreeC", "mean_annual_precipitation_mm", "air_temp_10day_sd_degreeC",
         "mean_hydraulic_residence_time_yrs", "catchment_size_km2", "latitude"),
         full_name = c("Maximum\ndepth", "Fetch", "Volume", "Surface\narea","Water clarity\n(Secchi depth)","Mean annual air\ntemperature", "Mean annual\nprecipitation","10-day variance in\n air temperature","Mean hydrologic\nresidence time","Catchment\nsize", "latitude"))
```

## RMSE at 10-days ahead

```{r}
horizon10rmse <- combined_1m %>% 
  filter(Model == "FLARE-GLM",
         horizon %in% c(1,10,20,30)) %>% 
  mutate(horizon = as.character(horizon)) %>% 
  select(Model, siteID, horizon, rmse)
```

## Slope of at RMSE over first 10-days

```{r}
slope10day <- combined_1m %>% 
  filter(Model == "FLARE-GLM") %>% 
  group_by(siteID, Model) %>% 
  summarize(rmse = max(rmse) - min(rmse), .groups = "drop") %>% 
  mutate(horizon = "slope") %>% 
  select(Model,siteID, horizon, rmse)
```

## Combine tables together

```{r}

horizon10rmse <- bind_rows(horizon10rmse, slope10day) %>% 
left_join(lake_info, by = "siteID") %>% 
   mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG")))
```

## Calculate correlations with lake characteristics


Correlations with 10-day ahead RMSE and 1-10 day RMSE slope. RMSE is multiplied by -1 so that smaller values equal less accuracy. This allows a positive correlation to mean that accuracy increases with the lake characteristic of interest

```{r}
horizon10rmse %>% 
  select(horizon, siteID, rmse, max_depth_m, fetch_m, volume_m3, surface_area_km2, mean_secchi_depth_m,
         mean_annual_temperature_degreeC, mean_annual_precipitation_mm, air_temp_10day_sd_degreeC,
         mean_hydraulic_residence_time_yrs, catchment_size_km2, latitude) %>% 
  pivot_longer(cols = -c("rmse","siteID", "horizon"), names_to = "variable", values_to = "value") %>% 
  left_join(variables) %>% 
  filter(horizon == "1") %>% 
    mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG"))) %>% 
  ggplot(aes(x = value, y = -rmse, col = siteID, shape = domain)) +
  geom_point() +
  facet_wrap(~full_name, scale = "free") +
  labs(y = "accuracy (-1 * RMSE)") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

```{r}
horizon10rmse %>% 
  select(siteID, rmse, horizon, max_depth_m, fetch_m, volume_m3, surface_area_km2, mean_secchi_depth_m,
         mean_annual_temperature_degreeC, mean_annual_precipitation_mm, air_temp_10day_sd_degreeC,
         mean_hydraulic_residence_time_yrs, catchment_size_km2, latitude) %>% 
  pivot_longer(cols = -c("siteID", "rmse","horizon"), names_to = "variable", values_to = "value") %>% 
  left_join(variables) %>% 
  filter(horizon == "slope") %>% 
  mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG"))) %>% 
  ggplot(aes(x = value, y = rmse, col = siteID, shape = domain)) +
  geom_point() +
  facet_wrap(~full_name, scale = "free", ncol = 2) +
  theme_bw() +
    labs(y = "rate of degradation (max RMSE - min RMSE)") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

```

Spearman

```{r}
spear_corr_table <- horizon10rmse %>% 
  select(rmse, horizon, max_depth_m, fetch_m, volume_m3, surface_area_km2, mean_secchi_depth_m,
         mean_annual_temperature_degreeC, mean_annual_precipitation_mm, air_temp_10day_sd_degreeC,
         mean_hydraulic_residence_time_yrs, catchment_size_km2, latitude) %>% 
  pivot_longer(cols = -c("rmse","horizon"), names_to = "variable", values_to = "value") %>% 
  group_by(variable, horizon) %>% 
  summarize(rho = cor(rmse, value, method = "spearman"),
            pvalue = cor.test(rmse, value, method = "spearman")$p.value, .groups = "drop") %>% 
  left_join(variables) %>% 
  filter(horizon %in% c("1", "slope")) %>% 
    mutate(Metric = ifelse(horizon == "1",  "accuracy", "accuracy\ndegradation"),
           rho = ifelse(Metric == "accuracy", -rho, rho)) %>%
   arrange(desc(abs(rho)))

corr_names <- rev(as.character(unique(spear_corr_table$full_name)))

spear_corr_table <- spear_corr_table %>%
  mutate(full_name = factor(full_name, levels = corr_names))
```
```{r}
domain_corr_table <- corr_table %>% arrange(variable) %>% 
  filter(variable %in% c("max_depth_m", "fetch_m", "volume_m3",
                         "surface_area_km2", "mean_secchi_depth_m",                      "mean_hydraulic_residence_time_yrs","catchment_size_km2")) %>% 
  select(variable, horizon, domain, rho) %>% 
  group_by(variable, horizon) %>% 
  summarize(max = max(rho),
            min = min(rho), .groups = "drop") %>% 
  filter(max == min)
```

# Generate Figures

## Figure 1

Figure 1 is the map.

## Figure 2

```{r}
y_label <- expression(paste('RMSE (',degree,'C)', sep = ""))
cbPalette <- c("#a50026", "#f46d43", "#fdae61", "#fee090","#74add1", "#313695")
  
p <- combined_1m %>% 
  filter(Model == "FLARE-GLM") %>% 
  mutate(horizon = as.numeric(horizon)) %>% 
  ggplot(aes(x = horizon, y = rmse, col = siteID, linetype = domain)) +
  geom_line(size=1) +
  ylim(0,3.75) +
  labs(x = "Horizon (days)", y = y_label, tag = "(a)", color = "NEON Site ID", linetype = "NEON Domain") +
  scale_linetype_manual(values=c("solid", "dashed", "dotted")) +
  scale_color_manual(values = cbPalette) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
                legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.key.width = unit(1, "cm"),
        legend.key.height = unit(0.3, "cm"),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        plot.tag.position = c(0.25,0.88))

p_skill <- combined_1m %>% 
  mutate(horizon = as.numeric(horizon)) %>% 
  mutate(domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast"))) %>% 
  pivot_wider(names_from = Model, values_from = rmse) %>% 
  mutate(rmse_skill =  (`Day-of-year mean` - `FLARE-GLM`)) %>% 
  ggplot(aes(horizon, rmse_skill, color = siteID, linetype = domain)) +
  geom_line(size=1) +
  geom_hline(aes(yintercept = 0)) +
  ylim(-1.1,3.2) +
  labs(x = "Horizon (days)", y = "RMSE Skill (Null - FLARE)", tag = "(b)", title = " ", color = "NEON Site ID", linetype = "NEON Domain") +
  annotate("text", x=20, y=3.1, label = "FLARE performs better", size = 3) +
  annotate("text", x=20, y=-1.1, label = "Null performs better", size = 3) +
  scale_color_manual(values = cbPalette) +
  theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed", "dotted")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.key.width = unit(1, "cm"),
        legend.key.height = unit(0.3, "cm"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.margin=margin(0,0,0,0),
        plot.tag.position = c(0.25,0.88))

p_combined <- p + p_skill + plot_layout(guides = 'collect') & theme(legend.position = "bottom") &   guides(color=guide_legend(nrow=2, title.position = "top"),linetype = guide_legend(nrow=3,byrow=TRUE, title.position = "top"))

p_combined
```
```{r}
ggsave(filename = file.path(lake_directory, "notebook","Figure2.jpg"), device = "jpeg", plot = p_combined, width = 4.5, height = 3.5, units = "in", dpi = 350)
```

## Figure 3

```{r} 
p <- spear_corr_table %>% 
  #mutate(rho = ifelse(abs(rho) >= 0.5, rho, NA)) %>% 
  #mutate(rho = ifelse(pvalue < 0.05, rho, NA)) %>% 
  filter(horizon %in% c("1","slope")) %>% 
  ggplot(aes(x = rho, y = full_name, col = Metric)) +
  geom_point() +
  geom_vline(xintercept = 0.5) +
  geom_vline(xintercept = -0.5) +
  geom_hline(yintercept = 4.5, linetype = "dashed") +
  xlim(-1,1) +
  labs(x = "Spearman's correlation coefficient", y = "variable") +
  scale_color_manual(values=c("red", "blue")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position= "bottom",
        axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(color = "black"))
p
```

```{r}
ggsave(filename = file.path(lake_directory, "notebook","Figure3.jpg"), device = "jpeg", plot = p, width = 4.5, height = 4.5, units = "in", dpi = 350)
```

## Values in text

Number of forecasts used in analysis
```{r}
length(unique(combined1$time))
combined2 %>% select(siteID, Model, horizon, depth) %>% filter(horizon == 1, Model == "FLARE-GLM", depth == 0.0) %>% group_by(siteID) %>% count()
```
```{r}
rmse_all_mean <- combined_1m %>% 
  filter(Model == "FLARE-GLM") %>% 
  arrange(desc(rmse))

rmse_all_mean
```



```{r}
clim_vs_flare_horizon <- combined_1m %>% 
  select(-domain) %>% 
  pivot_wider(names_from = Model, values_from = rmse) %>%
  mutate(diff = `Day-of-year mean` - `FLARE-GLM`) %>%
  filter(diff < 0) %>%
  group_by(siteID) %>%
  summarize(min = min(horizon, na.rm = TRUE))
clim_vs_flare_horizon
```


```{r}
rmse_site_mean <- combined_1m %>% 
  filter(Model == "FLARE-GLM") %>%
  select(-domain) %>% 
  #pivot_wider(names_from = siteID, values_from = rmse) %>% 
  filter(horizon %in% c(1, 7, 21, 34)) %>% 
  mutate(horizon = as.numeric(horizon)) %>% 
  group_by(horizon) %>% 
  summarize(min = min(rmse),
            max = max(rmse),
            mean = mean(rmse))
rmse_site_mean %>% 
  arrange(horizon)

```


```{r}
d <- horizon10rmse %>% 
  filter(horizon == "slope") %>% 
  mutate(domain = ifelse(domain == "Southeast", "south", "north")) %>% 
  group_by(domain) %>% 
  summarize(mean = mean(rmse)) %>% 
  pivot_wider(names_from = domain, values_from = mean)

d$north/d$south

  
  
```


```{r}
d1 <- domain_corr_table %>% 
  mutate(direction = ifelse(max == 1, 1, -1)) %>% 
  mutate(analysis = "domain") %>% 
  mutate(rho = NA,
         pvalue = NA) %>% 
  select(variable, analysis, direction, horizon, rho, pvalue)
d2 <- spear_corr_table %>% 
  filter(abs(rho) > 0.5) %>%   
  mutate(direction = ifelse(rho > 0, 1, -1))%>% 
  mutate(analysis = "spearmen")%>% 
  select(variable, analysis, direction, horizon, rho, pvalue)

d <- bind_rows(d1,d2) %>% 
  rename(metric = horizon) %>% 
  mutate(metric = ifelse(metric == 1, "accuracy","degradation")) %>% 
  arrange(metric, variable)

d

```

#Supplemental Information Figures

## Figure SI1 (all depths)

Averaging all scores for all depths within each lake

```{r}
y_label <- expression(paste('RMSE (',degree,'C)', sep = ""))
p1 <- combined_all_depths %>% 
  filter(Model == "FLARE-GLM") %>% 
  mutate(horizon = as.numeric(horizon)) %>% 
  ggplot(aes(x = horizon, y = rmse, col = siteID, linetype = domain)) +
  geom_line(size = 1) +
  ylim(0,4) +
  labs(x = "Horizon (days)", y = y_label, tag = "(a)", color = "NEON Site ID", linetype = "NEON Domain") +
  scale_color_manual(values = cbPalette) +
  scale_linetype_manual(values=c("solid", "dashed", "dotted")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.width = unit(1, "cm"),
        legend.key.height = unit(0.2, "cm"),
        legend.text = element_text(size = 7.5),
        legend.title = element_text(size = 7.5),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        plot.tag.position = c(0.25,0.93)) +
  guides(color=guide_legend(nrow=2,byrow=TRUE, 
                            title.position = "top"),
         linetype = guide_legend(nrow=2,byrow=TRUE, 
                                 title.position = "top")) 

y_label <- expression(paste('Continous Ranked Probability Score (',degree,'C)', sep = ""))
p2 <- combined_1m_crps %>% 
  filter(Model == "FLARE-GLM") %>% 
  mutate(horizon = as.numeric(horizon)) %>% 
  ggplot(aes(x = horizon, y = crps, col = siteID, linetype = domain)) +
  geom_line(size = 1) +
  ylim(0,1.75) +
  labs(x = "Horizon (days)", y = y_label, tag = "(b)", color = "NEON Site ID", linetype = "NEON Domain") +
  scale_color_manual(values = cbPalette) +
  scale_linetype_manual(values=c("solid", "dashed", "dotted")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.width = unit(1, "cm"),
        legend.key.height = unit(0.2, "cm"),
        legend.text = element_text(size = 7.5),
        legend.title = element_text(size = 7.5),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        plot.tag.position = c(0.3,0.93)) +
  guides(color=guide_legend(nrow=2,byrow=TRUE, 
                            title.position = "top"),
         linetype = guide_legend(nrow=2,byrow=TRUE, 
                                 title.position = "top")) 

p3 <- p1 + p2 + plot_layout(guides = 'collect') & theme(legend.position = "bottom") &   guides(color=guide_legend(nrow=2, title.position = "top"),linetype = guide_legend(nrow=2,byrow=TRUE, title.position = "top"))

ggsave(filename = file.path(lake_directory, "notebook","FigureS1.jpg"), device = "jpeg", plot = p3, width = 4.5, height = 4.0, units = "in", dpi = 350)
```



```{r}
y_label <- expression(paste('Accurancy (-RMSE) (',degree,'C)', sep = ""))
cbPalette <- c("#a50026", "#f46d43", "#fdae61", "#fee090","#74add1", "#313695")
p4 <- horizon10rmse %>% 
  select(horizon, siteID, rmse, max_depth_m, fetch_m, volume_m3, surface_area_km2, mean_secchi_depth_m,
         mean_annual_temperature_degreeC, mean_annual_precipitation_mm, air_temp_10day_sd_degreeC,
         mean_hydraulic_residence_time_yrs, catchment_size_km2, latitude) %>% 
  pivot_longer(cols = -c("rmse","siteID", "horizon"), names_to = "variable", values_to = "value") %>% 
  left_join(variables) %>% 
  filter(horizon == "1") %>% 
    mutate(domain = NA,
         domain = ifelse(siteID %in% c("BARC","SUGG"), "Southeast", domain),
         domain = ifelse(siteID %in% c("CRAM","LIRO"), "Great Lakes", domain),
         domain = ifelse(siteID %in% c("PRLA","PRPO"), "Northern Plains", domain),
         domain = factor(domain, levels = c("Northern Plains","Great Lakes","Southeast")),
         siteID = factor(siteID, levels = c("PRLA","PRPO","CRAM","LIRO","BARC","SUGG"))) %>% 
  ggplot(aes(x = value, y = -rmse, col = siteID, shape = domain)) +
  geom_point() +
  scale_color_manual(values = cbPalette) +
  facet_wrap(~full_name, scale = "free", ncol = 2) +
  labs(y = "accuracy (-1 * RMSE)") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(),
        legend.position = "bottom")
ggsave(filename = file.path(lake_directory, "notebook","FigureS2.jpg"), device = "jpeg", plot = p4, width = 4.5, height = 7.5, units = "in", dpi = 350)
```
